Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-07-18 Manuscript/main.tex
Worked on partial plots

\documentclass[12pt, draft]{article} % use larger type; default would be 10pt

@@

%Visits/hr: In GP, 3.1 in 2014, 10.6 in 2015; in LB 5.9 in 2014, 4.5 in 2015
\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeNumHivesDistVis.png}
    \caption[Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields]{Partial effect of distance away from field edge and stocking on honey bee visitation in commodity canola fields. Solid lines represents median, and shaded areas represent 95\% CIs. Red line represents overall slope (controlling for region and year).}
    \label{fig:hbeeDist_commodity}
\end{figure}
%PERHAPS INCLUDE FIGURE OF AREA/YEAR EFFECTS IN THE SUPPLEMENTAL?

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeHbeeDist_both.png}
    \caption[Partial effect of distance from field edge on bee visitation in seed canola fields]{Partial effect of distance from field edge on honey bee and leafcutter bee visitation in seed canola fields. Solid lines represent medians, and shaded areas represent 95\% CIs.}
    \label{fig:hbeeDist_both}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeLbeeDistBothBees.png}
    \caption[Partial effect of distance from leafcutter shelter on bee visitation in seed canola fields]{Partial effect of distance from leafcutter shelter on honey bee and leafcutter bee visitation in seed canola fields. Solid lines represent medians, and shaded areas represent 95\% CIs.}
    \label{fig:lbeeDist_both}
\end{figure} %SH: WOULD BE COOL TO HAVE A ``SUM OF BOTH BEES" LINE AS WELL - perhaps in the manusript? may require a separate model of both bees, or possibly just adding model results together

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{slopeEdgeCent_both.png}
    \caption[Partial effect of bay position on honey bee and leafcutter bee visitation]{Partial effect of bay position (edge or centre of female bay) on honey bee and leafcutter bee visitation. Coloured points represents median value, and vertical bars represent 95\% CIs.}
    \label{fig:edgeCentVis_both}
\end{figure}

>>>>

\documentclass[12pt]{article} % use larger type; default would be 10pt

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth,keepaspectratio=true]{../Figures/allVisits.png}
    \caption{Effect of distance from a) honey bee apiaries and b) leafcutter shelters on visitation rate. Visitation rates in commodity fields are shown at a stocking rate of 40 hives (black line), while stocking rates are at 160 hives in seed fields (yellow line).}
    \label{fig:hbeeDist_commodity}
\end{figure}
